---
title: "Alcohol vs Seat choice"
author: "Lucille McEwen"
date: "September 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??
$H_0$ There is no difference in alcohol consumption based on seat choice.  
$H_A$ There is a difference in alcohol consumption based on seat choice.   
  
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys
```{r}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```  
  
## Conclusions  
There is not a difference in the front-back and middle-back seats but the middle-front is different from both the previous two. 

The p-value is 0.000116 which is less than 0.5, so we reject the null hypothesis. There is a difference in alcohol consumption based on seat choice. 

